# ---
# title: "iHg - Markov chain Monte Carlo Calibration Diagnosis"
# author: "YS Lin and NH Hsieh" 
# date: "2023/02/05 (update: `r Sys.Date()`)"
# output: 
#  html_document:
# fig_caption: yes  
# ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('..')
wd <- getwd()
knitr::opts_knit$set(root.dir =  wd)
```

# 0 Prerequisites
```{r, include=FALSE}
source("MCSim/function.R")
getwd()
```

# Import the R packages
```{r}
library(tidyverse, quietly=T)
library(rstan, quietly=T)
library(bayesplot, quietly=T)
library(corrplot, quietly=T)
library(sensitivity, quietly=T)
library(pksensi, quietly=T)
library(data.table, quietly=T)
library(coda, quietly=T)
library(ggplot2, quietly=T)
library(ggcorrplot, quietly=T)
theme_set(theme_bw())
```

# traceplot and density diagnosis (every 10th sample from last half of MCMMC runs #############
```{r, eval=F}
Humanjob1 <- fread("outputs/iHgHuman_4880.out")|> as.data.frame()
Humanjob2 <- fread("outputs/iHgHuman_3365.out")|> as.data.frame()
Humanjob3 <- fread("outputs/iHgHuman_5916.out")|> as.data.frame()
Humanjob4 <- fread("outputs/iHgHuman_6734.out")|> as.data.frame()
Human_x <- mcmc_array(data = list(Humanjob1, Humanjob2, Humanjob3, Humanjob4))
str <- ceiling(nrow(Human_x)/2) + 1
end <- nrow(Human_x)
j <- c(str:end) # discard burn-in
sample_x <- seq(150001, 300000, 10)
Human_x2 <- Human_x[sample_x,,]
mcmc_Human <- Human_x2 
save(mcmc_Human, file = "mcmc_Human.RData")

pars_Pop <- c("M_lnPLC(1)", "M_lnPKC(1)", "M_lnPBrnC(1)",	"M_lnPRestC(1)",	"M_lnKabsC(1)",	"M_lnKunabsC(1)",	"M_lnKbileC(1)",	"M_lnKurineC(1)",	"M_lnKbrnC(1)")
tp_Human <-bayesplot::mcmc_trace(Human_x2 [,,], pars = pars_Pop)
dp_Human <-bayesplot::mcmc_dens_overlay(Human_x2 [,,],  pars = pars_Pop)
ggplot2::ggsave(filename = "plots/suppl/Figure_S3_traceplot_Human.eps", 
                plot = tp_Human, 
                device = cairo_ps, 
                dpi = 1200, 
                width = 15,
                height = 10, 
                units = "cm")

ggplot2::ggsave(filename = "plots/suppl/Figure_S6_density_Human.eps", 
                plot = dp_Human, 
                device = cairo_ps, 
                dpi = 1200, 
                width = 15,
                height = 10, 
                units = "cm")
```

# Andrew Gelman Scale Reduction Factor
```{r}
Humanmonitor <-monitor(Human_x, digits=4, probs = c(0.025, 0.5, 0.975), warmup = floor(dim(Human_x)[1]/2))
print(Humanmonitor)
dim(Human_x)
```

#  MPSRF
```{r}
Humanjob1 = as.mcmc(fread("outputs/iHgHuman_4880.out") |> as.data.frame(), header=T) 
Humanjob2 = as.mcmc(fread("outputs/iHgHuman_3365.out") |> as.data.frame(), header=T) 
Humanjob3 = as.mcmc(fread("outputs/iHgHuman_5916.out") |> as.data.frame(), header=T) 
Humanjob4 = as.mcmc(fread("outputs/iHgHuman_6734.out") |> as.data.frame(), header=T) 

x1Human <- Humanjob1[,2:39  , drop=FALSE]
x2Human <- Humanjob2[,2:39  , drop=FALSE]
x3Human <- Humanjob3[,2:39  , drop=FALSE]
x4Human <- Humanjob4[,2:39  , drop=FALSE]

combined = mcmc.list(x1Human,x2Human,x3Human,x4Human) 
gelman.diag(combined, autoburnin=TRUE, multivariate=TRUE)
```
# Correlation matrix of population posterior iHg-specific parameters 
```{r}
sim1.1 <- fread("outputs/iHgHuman_3365.out") 
sim2.1 <- fread("outputs/iHgHuman_4880.out") 
sim3.1 <- fread("outputs/iHgHuman_5916.out") 
sim4.1 <- fread("outputs/iHgHuman_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Human_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Human_corr)

pars_name <- dimnames(Human_corr)[[3]]
str <- which(pars_name == "M_lnPLC(1)")
end <- which(pars_name == "M_lnKbrnC(1)")
j <- c(str:end) 
M_pars <- pars_name[str:end]
sample_x <- seq(150001, 300000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Human_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  GGally::  ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha = TRUE) +
  theme_minimal() + labs(title = "Human") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Figure_S9_Correlation_matrix_Human.pdf", dpi = 1200, height = 10, width = 15, units="in")
```

```{r, include=FALSE}
clear()
```
