# ---
# title: "iHg - Markov chain Monte Carlo Calibration Diagnosis for mouse"
# author: "YS Lin and NH Hsieh" 
# date: "2023/04/01 (update: `r Sys.Date()`)"
# output: 
#  html_document:
# fig_caption: yes  
# ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('..')
wd <- getwd()
knitr::opts_knit$set(root.dir =  wd)
```

# 0 Prerequisites
```{r, include=FALSE}
source("MCSim/function.R")
getwd()
```

# Import the R packages
```{r}
library(tidyverse, quietly=T)
library(rstan, quietly=T)
library(bayesplot, quietly=T)
library(coda, quietly=T)
library(corrplot, quietly=T)
library(sensitivity, quietly=T)
library(pksensi, quietly=T)
library(data.table, quietly=T)
library(GGally, quietly=T)
library(ggplot2, quietly=T)
library(ggcorrplot, quietly=T)
theme_set(theme_bw())
```

# traceplot and density diagnosis (every 10th sample from last half of MCMMC runs #############
# This section will produce Supplemental Figure S2 and Figure S5
```{r, eval=F}
Mousejob1 <- fread("outputs/iHgMouse_4880.out")|> as.data.frame()
Mousejob2 <- fread("outputs/iHgMouse_3365.out")|> as.data.frame()
Mousejob3 <- fread("outputs/iHgMouse_5916.out")|> as.data.frame()
Mousejob4 <- fread("outputs/iHgMouse_6734.out")|> as.data.frame()
Mouse_x <- mcmc_array(data = list(Mousejob1, Mousejob2, Mousejob3, Mousejob4))
str <- ceiling(nrow(Mouse_x)/2) + 1
end <- nrow(Mouse_x)
j <- c(str:end) # discard burn-in
sample_x <- seq(50001, 100000, 10)
Mouse_x2 <- Mouse_x[sample_x,,]
mcmc_Mouse <- Mouse_x2 
save(mcmc_Mouse, file = "mcmc_Mouse.RData")

pars_Pop <- c("M_lnPLC(1)", "M_lnPKC(1)", "M_lnPBrnC(1)",	"M_lnPRestC(1)",	"M_lnKabsC(1)",	"M_lnKunabsC(1)",	"M_lnKbileC(1)",	"M_lnKurineC(1)",	"M_lnKbrnC(1)")
tp_Mouse <-bayesplot::mcmc_trace(Mouse_x2 [,,], pars = pars_Pop)
dp_Mouse <-bayesplot::mcmc_dens_overlay(Mouse_x2 [,,],  pars = pars_Pop)
ggplot2::ggsave(filename = "plots/suppl/Figure_S2_traceplot_Mouse.eps", 
                plot = tp_Mouse, 
                device = cairo_ps, 
                dpi = 1200, 
                width = 15,
                height = 10, 
                units = "cm")

ggplot2::ggsave(filename = "plots/suppl/Figure_S5_density_Mouse.eps", 
                plot = dp_Mouse, 
                device = cairo_ps, 
                dpi = 1200, 
                width = 15,
                height = 10, 
                units = "cm")
```

# ---
# Andrew Gelman Scale Reduction Factor**  
# This section produces results for the posterior distributions shown in Supplemental Tables S5 and S8.  
#  
# From Supplemental Table S5, one can exponentiate each scaling coefficient parameter to obtain the posterior estimate as presented in Table 
# (e.g., exp(lnPLC) = exp(2.079) = 7.99, where PLC is the liver:blood partition coefficient for mice).  
#  
# For Supplemental Table S8, the residual error geometric standard deviation was estimated as the exponential of 
# the square root of the error term (e.g., for "Ve_Aurine," representing urine).
# ---
```{r}
Mousemonitor <-monitor(Mouse_x, digits=4, probs = c(0.025, 0.5, 0.975), warmup = floor(dim(Mouse_x)[1]/2))
print(Mousemonitor)
dim(Mouse_x)
```

# MPSRF
# This section will produce MPSRF values for Supplemental Figure S2 traceplot
```{r}
Mousejob1 = as.mcmc(fread("outputs/iHgMouse_4880.out") |> as.data.frame(), header=T) 
Mousejob2 = as.mcmc(fread("outputs/iHgMouse_3365.out") |> as.data.frame(), header=T) 
Mousejob3 = as.mcmc(fread("outputs/iHgMouse_5916.out") |> as.data.frame(), header=T) 
Mousejob4 = as.mcmc(fread("outputs/iHgMouse_6734.out") |> as.data.frame(), header=T) 

x1Mouse <- Mousejob1[,2:60  , drop=FALSE]
x2Mouse <- Mousejob2[,2:60  , drop=FALSE]
x3Mouse <- Mousejob3[,2:60  , drop=FALSE]
x4Mouse <- Mousejob4[,2:60  , drop=FALSE]

combined = mcmc.list(x1Mouse,x2Mouse,x3Mouse,x4Mouse) 
gelman.diag(combined, autoburnin=TRUE, multivariate=TRUE)
```

# Correlation matrix of population posterior iHg-specific parameters 
# This section will produce Supplemental Figure S8 plot
```{r}
sim1.1 <- fread("outputs/iHgMouse_3365.out") 
sim2.1 <- fread("outputs/iHgMouse_4880.out") 
sim3.1 <- fread("outputs/iHgMouse_5916.out") 
sim4.1 <- fread("outputs/iHgMouse_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Mouse_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Mouse_corr)

pars_name <- dimnames(Mouse_corr)[[3]]
str <- which(pars_name == "M_lnPLC(1)")
end <- which(pars_name == "M_lnKbrnC(1)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Mouse_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  GGally:: ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha = TRUE) +
  theme_minimal() + labs(title = "Mouse") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Figure_S8_Correlation_matrix_Mouse.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
#
# ------------------------------------------------------------------------
#  The following shows study-level posterior iHg-specific parameters for mice 
# ------------------------------------------------------------------------
#
#
# Correlation matrix of study-level posterior iHg-specific parameters ---- Aaseth 1982
# For Aaseth 1982, the exposure scenario involves a single IV dose of 400 µg Hg/kg (2 µmol Hg/kg) in mice. 
# This study is labeled as Study 1.1, as it is listed as the first study in the mouse analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgMouse_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgMouse_3365.out") 
sim2.1 <- fread("outputs/iHgMouse_4880.out") 
sim3.1 <- fread("outputs/iHgMouse_5916.out") 
sim4.1 <- fread("outputs/iHgMouse_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Mouse_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Mouse_corr)

pars_name <- dimnames(Mouse_corr)[[3]]
str <- which(pars_name == "lnPLC(1.1)")
end <- which(pars_name == "lnKbrnC(1.1)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Mouse_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  GGally:: ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha = TRUE) +
  theme_minimal() + labs(title = "Mouse") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Mouse_Correlation_Aaseth_1982.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
# Correlation matrix of study-level posterior iHg-specific parameters ---- Nielsen 1992
# For Nielsen 1992, exposure scenario is a single oral dose of 1000 ug Hg/kg for mouse (labelled as Study 1.2 as it is list as the second study in the mouse analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgMouse_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgMouse_3365.out") 
sim2.1 <- fread("outputs/iHgMouse_4880.out") 
sim3.1 <- fread("outputs/iHgMouse_5916.out") 
sim4.1 <- fread("outputs/iHgMouse_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Mouse_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Mouse_corr)

pars_name <- dimnames(Mouse_corr)[[3]]
str <- which(pars_name == "lnPLC(1.2)")
end <- which(pars_name == "lnKbrnC(1.2)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Mouse_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  GGally:: ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha = TRUE) +
  theme_minimal() + labs(title = "Mouse") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Mouse_Correlation_Nielsen_1992.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
# Correlation matrix of study-level posterior iHg-specific parameter ---- Dieter 1983
# For Dieter 1983, exposure scenario is daily oral gavage of 3,000-75,000 ug Hg/kg for mouse (labelled as Study 1.3 as it is list as the third study in the mouse analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgMouse_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgMouse_3365.out") 
sim2.1 <- fread("outputs/iHgMouse_4880.out") 
sim3.1 <- fread("outputs/iHgMouse_5916.out") 
sim4.1 <- fread("outputs/iHgMouse_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Mouse_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Mouse_corr)

pars_name <- dimnames(Mouse_corr)[[3]]
str <- which(pars_name == "lnPLC(1.3)")
end <- which(pars_name == "lnKbrnC(1.3)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Mouse_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  GGally:: ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha = TRUE) +
  theme_minimal() + labs(title = "Mouse") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Mouse_Correlation_Dieter_1983.jpg", dpi = 600, height = 10, width = 15, units="in")
```

# Correlation matrix of study-level posterior iHg-specific parameter ---- Ntp 1993
# For Ntp 1993, exposure scenario is daily oral gavage of 925-14,775 ug Hg/kg for mouse (labelled as Study 1.4 as it is list as the fourth study in the mouse analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgMouse_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgMouse_3365.out") 
sim2.1 <- fread("outputs/iHgMouse_4880.out") 
sim3.1 <- fread("outputs/iHgMouse_5916.out") 
sim4.1 <- fread("outputs/iHgMouse_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Mouse_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Mouse_corr)

pars_name <- dimnames(Mouse_corr)[[3]]
str <- which(pars_name == "lnPLC(1.4)")
end <- which(pars_name == "lnKbrnC(1.4)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Mouse_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  GGally:: ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha = TRUE) +
  theme_minimal() + labs(title = "Mouse") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Mouse_Correlation_Ntp_1993.jpg", dpi = 600, height = 10, width = 15, units="in")
```

```{r, include=FALSE}
clear()
```
