# ---
# title: "iHg - Markov chain Monte Carlo Calibration Diagnosis for rat"
# author: "YS Lin and NH Hsieh" 
# date: "2023/04/01 (update: `r Sys.Date()`)"
# output: 
#  html_document:
# fig_caption: yes  
# ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=T)
setwd('..')
wd <- getwd()
knitr::opts_knit$set(root.dir =  wd)
```

# 0 Prerequisites
```{r, include=FALSE}
source("MCSim/function.R")
getwd()
```

# Import the R packages
```{r}
library(tidyverse, quietly=T)
library(rstan, quietly=T)
library(bayesplot, quietly=T)
library(coda, quietly=T)
library(corrplot, quietly=T)
library(sensitivity, quietly=T)
library(pksensi, quietly=T)
library(data.table, quietly=T)
library(GGally, quietly=T)
library(ggplot2, quietly=T)
library(ggcorrplot, quietly=T)
theme_set(theme_bw())
```

# traceplot and density diagnosis (every 10th sample from last half of MCMMC runs #############
# This section will produce Supplemental Figure S3 and Figure S6
```{r, eval=F}
Ratjob1 <- fread("outputs/iHgRat_4880.out")|> as.data.frame()
Ratjob2 <- fread("outputs/iHgRat_3365.out")|> as.data.frame()
Ratjob3 <- fread("outputs/iHgRat_5916.out")|> as.data.frame()
Ratjob4 <- fread("outputs/iHgRat_6734.out")|> as.data.frame()
Rat_x <- mcmc_array(data = list(Ratjob1, Ratjob2, Ratjob3, Ratjob4))
str <- ceiling(nrow(Rat_x)/2) + 1
end <- nrow(Rat_x)
j <- c(str:end) # discard burn-in
sample_x <- seq(50001, 100000, 10)
Rat_x2 <- Rat_x[sample_x,,]
mcmc_Rat <- Rat_x2 
save(mcmc_Rat, file = "mcmc_Rat.RData")

pars_Pop <- c("M_lnPLC(1)", "M_lnPKC(1)", "M_lnPBrnC(1)",	"M_lnPRestC(1)",	"M_lnKabsC(1)",	"M_lnKunabsC(1)",	"M_lnKbileC(1)",	"M_lnKurineC(1)",	"M_lnKbrnC(1)")
tp_Rat <-bayesplot::mcmc_trace(Rat_x2 [,,], pars = pars_Pop)
dp_Rat <-bayesplot::mcmc_dens_overlay(Rat_x2 [,,],  pars = pars_Pop)
ggplot2::ggsave(filename = "plots/suppl/Figure_S3_traceplot_Rat.eps", 
                plot = tp_Rat, 
                device = cairo_ps, 
                dpi = 1200, 
                width = 15,
                height = 10, 
                units = "cm")

ggplot2::ggsave(filename = "plots/suppl/Figure_S6_density_Rat.eps", 
                plot = dp_Rat, 
                device = cairo_ps, 
                dpi = 1200, 
                width = 15,
                height = 10, 
                units = "cm")
```

# ---
# Andrew Gelman Scale Reduction Factor**  
# This section produces results for the posterior distributions shown in Supplemental Tables S6 and S9.  
#  
# From Supplemental Table S6, one can exponentiate each scaling coefficient parameter to obtain the posterior estimate as presented in Table 
# (e.g., exp(lnPLC) = exp(1.753) = 7.99, where PLC is the liver:blood partition coefficient for rat).  
#  
# For Supplemental Table S9, the residual error geometric standard deviation was estimated as the exponential of 
# the square root of the error term (e.g., for "Ve_Aurine," representing urine).
# ---
```{r}
Ratmonitor <-monitor(Rat_x, digits=4, probs = c(0.025, 0.5, 0.975), warmup = floor(dim(Rat_x)[1]/2))
print(Ratmonitor)
dim(Rat_x)
```

# MPSRF
# This section will produce MPSRF values for Supplemental Figure S3 traceplot
```{r}
Ratjob1 = as.mcmc(fread("outputs/iHgRat_4880.out") |> as.data.frame(), header=T) 
Ratjob2 = as.mcmc(fread("outputs/iHgRat_3365.out") |> as.data.frame(), header=T) 
Ratjob3 = as.mcmc(fread("outputs/iHgRat_5916.out") |> as.data.frame(), header=T) 
Ratjob4 = as.mcmc(fread("outputs/iHgRat_6734.out") |> as.data.frame(), header=T) 

x1Rat <- Ratjob1[,2:61, drop=FALSE]
x2Rat <- Ratjob2[,2:61, drop=FALSE]
x3Rat <- Ratjob3[,2:61, drop=FALSE]
x4Rat <- Ratjob4[,2:61, drop=FALSE]

combined = mcmc.list(x1Rat,x2Rat,x3Rat,x4Rat) 
gelman.diag(combined, autoburnin=TRUE, multivariate=TRUE)
```

# Correlation matrix of population posterior iHg-specific parameters 
# This section will produce Supplemental Figure S9 plot
```{r}
sim1.1 <- fread("outputs/iHgRat_3365.out") 
sim2.1 <- fread("outputs/iHgRat_4880.out") 
sim3.1 <- fread("outputs/iHgRat_5916.out") 
sim4.1 <- fread("outputs/iHgRat_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Rat_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Rat_corr)

pars_name <- dimnames(Rat_corr)[[3]]
str <- which(pars_name == "M_lnPLC(1)")
end <- which(pars_name == "M_lnKbrnC(1)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Rat_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  # GGally::
  ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha=T) +
  theme_minimal() + labs(title = "Rat") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Figure_S9_Correlation_matrix_Rat.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
#
# ------------------------------------------------------------------------
#  The following shows study-level posterior iHg-specific parameters for rats 
# ------------------------------------------------------------------------
#
#
# Correlation matrix of study-level posterior iHg-specific parameter ---- Rothstein 1960
# For Rothstein 1960, exposure scenario is a single IV dose of 250 ug Hg/kg for rats. 
# This study is labeled as Study 1.1, as it is listed as the first study in the rat analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgRat_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgRat_3365.out") 
sim2.1 <- fread("outputs/iHgRat_4880.out") 
sim3.1 <- fread("outputs/iHgRat_5916.out") 
sim4.1 <- fread("outputs/iHgRat_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Rat_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Rat_corr)

pars_name <- dimnames(Rat_corr)[[3]]
str <- which(pars_name == "lnPLC(1.1)")
end <- which(pars_name == "lnKbrnC(1.1)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Rat_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  # GGally::
  ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha=T) +
  theme_minimal() + labs(title = "Rat") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Rat_Correlation_Rothstein_1960.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
# Correlation matrix of study-level posterior iHg-specific parameter ---- Oriquat 2013
# For Oriquat 2013, exposure scenario is a twice weekly of 2770 ug Hg/kg for rats. 
# This study is labeled as Study 1.2, as it is listed as the second study in the rat analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgRat_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgRat_3365.out") 
sim2.1 <- fread("outputs/iHgRat_4880.out") 
sim3.1 <- fread("outputs/iHgRat_5916.out") 
sim4.1 <- fread("outputs/iHgRat_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Rat_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Rat_corr)

pars_name <- dimnames(Rat_corr)[[3]]
str <- which(pars_name == "lnPLC(1.2)")
end <- which(pars_name == "lnKbrnC(1.2)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Rat_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  # GGally::
  ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha=T) +
  theme_minimal() + labs(title = "Rat") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Rat_Correlation_Oriquat_2013.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
# Correlation matrix of study-level posterior iHg-specific parameter ---- Morcillo 1995
# For Morcillo 1995, exposure scenario is daily drinking water of 100-7200 ug/kg/day for rats. 
# This study is labeled as Study 1.3, as it is listed as the third study in the rat analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgRat_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgRat_3365.out") 
sim2.1 <- fread("outputs/iHgRat_4880.out") 
sim3.1 <- fread("outputs/iHgRat_5916.out") 
sim4.1 <- fread("outputs/iHgRat_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Rat_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Rat_corr)

pars_name <- dimnames(Rat_corr)[[3]]
str <- which(pars_name == "lnPLC(1.3)")
end <- which(pars_name == "lnKbrnC(1.3)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Rat_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  # GGally::
  ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha=T) +
  theme_minimal() + labs(title = "Rat") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Rat_Correlation_Morcillo_1995.jpg", dpi = 600, height = 10, width = 15, units="in")
```
#
# Correlation matrix of study-level posterior iHg-specific parameter ---- NTP 1993
# For NTP 1993, exposure scenario is daily gavage of 230-3,695 ug/kg/day for rats. 
# This study is labeled as Study 1.4, as it is listed as the fourth study in the rat analysis. 
# See the MCMC input file in the "MCMC replication" folder for details (e.g., iHgRat_3365.in).
#

```{r}
sim1.1 <- fread("outputs/iHgRat_3365.out") 
sim2.1 <- fread("outputs/iHgRat_4880.out") 
sim3.1 <- fread("outputs/iHgRat_5916.out") 
sim4.1 <- fread("outputs/iHgRat_6734.out") 

SIM1 <- do.call(rbind, list(sim1.1))
SIM2 <- do.call(rbind, list(sim2.1))
SIM3 <- do.call(rbind, list(sim3.1))
SIM4 <- do.call(rbind, list(sim4.1))

Rat_corr <-mcmc_array(list(SIM1, SIM2, SIM3, SIM4))
#dim(Rat_corr)

pars_name <- dimnames(Rat_corr)[[3]]
str <- which(pars_name == "lnPLC(1.4)")
end <- which(pars_name == "lnKbrnC(1.4)")
M_pars <- pars_name[str:end]
sample_x <- seq(50001, 100000, 10)
Parameter <- c(M_pars) %>%
  strsplit(split =  "\\(1\\)") %>% unlist()
# Correlation matrix
sum_chains <- length(j)*4

Rat_corr[j,,M_pars] %>% matrix(nrow = sum_chains) %>%
  `colnames<-`(Parameter[1:9])  %>% 
  # GGally::
  ggcorr(nbreaks = 5, label = T, label_size = 4, label_round = 2, size = 4, label_alpha=T) +
  theme_minimal() + labs(title = "Rat") + theme(plot.title = element_text(size=24, hjust = 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), title = element_blank()) +   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 
ggsave("plots/suppl/Rat_Correlation_NTP_1993.jpg", dpi = 600, height = 10, width = 15, units="in")
```


```{r, include=FALSE}
clear()
```
